Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-09-26 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

            Let $(g, \omega, A)$ satisfies Assumptiom \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 

@@

        Next, let's explore some options for minimizing the duality gap of the proximal problem. 

@@

        Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfies for all $k \ge 0$: 

@@

        When, $k = 1$ it instead have: 

@@

                + \mathcal E_0 \sum_{i = 1}^{k} \frac{1}{n^p}

@@

        Conside results from Lemma \ref{lemma:inxt-apg-cnvg-prep1} has $\forall k \ge 1$: 

@@

            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 

@@

        Therefore it points to the following inequality: 

@@

>>>>

            Let $(g, \omega, A)$ satisfies assumption \ref{ass:for-inxt-prox}, $\epsilon \ge 0$, then 

@@

        The following fact from the literature indicates that it's sufficient to minimize the dual problem $\Psi_\lambda$ to obtain an element of the inexact proximal point operator. 
        The following fact is Proposition \cite[Theorem 5.1]{villa_accelerated_2013}. 
        \begin{fact}[minimizing dual of the proximal problem]
            Let $\bar v$ be a solution of $\Psi$. 
            Suppose that $(v_n)_{n \ge 0}$ is a minimizing sequence for $\Psi$. 
            Let $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$. 
            If in addition, $\Phi_\lambda$ is $L_1$ Lipschitz continuous, then it has for all $k \ge 0$ the inequality: 
                \Phi_{\lambda}(z_n) - \Phi_\lambda(\bar x) 
                &\le L_1 \Vert z_n - \bar z\Vert 
                \le L_1\sqrt{2\lambda}(\Psi_\lambda(v_n) - \Psi_\lambda(\bar v))^{1/2}. 
        We remark that the above fact translates any algorithm that optimizes the function value of the dual problem into optimizing duality gap $\mathbf G(z_n, v_n)$. 
        For this reasons, the inner loop interation required to achieve $\mathbf G(z_n, v_n) < \epsilon$ is now related to the convergence rate of the algorithms used to optimize $\Psi_\lambda(v_n)$. 

@@

        Given any initial condition $v_{-1}, x_{-1} \in \RR^n$, the algorithm generates the sequences $(y_k, x_k, v_k)_{k \ge 0}$ such that they satisfy for all $k \ge 0$: 

@@

        When, $k = 1$ it instead has: 

@@

                + \mathcal E_0 \sum_{n = 1}^{k} \frac{1}{n^p}

@@

        Consider results from Lemma \ref{lemma:inxt-apg-cnvg-prep1} has $\forall k \ge 1$: 

@@

            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le (\rho_k/2)\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 

@@

        Therefore, it points to the following inequality: 

@@

\section{Linear convergence for the inner loop proximal problem}

### 2025-09-26 Notebook LaTEX/R-WAPG/presentation-shorter.tex
>w<, changes

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
}
\date[\today]{\today \\ \vspace{1cm} \tiny{Joint work with Shawn/Xianfu Wang}}
\subject{Nesterov's acceleration and its applications}

@@

            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$. 
            Then they satisfy for all $k\ge 1$: 

@@

            Fix any arbitrary $x^* \in \RR^n, N \in \mathbb N$.

@@

            Then for all $k = 1, 2, \ldots, N$:

>>>>

\title{
    Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations
}
% \newcommand{\email}{lalala@lala.la}
\institute[UBCO]{
    University of British Columbia Okanagan
    \\
    WCOM 2025
}
\date[\today]{
    \today \\ \vspace{1cm} 
    \tiny{Joint work with Shawn/Xianfu Wang}\\ 
    \tiny{The research of HL and XW was partially supported by the NSERC Discovery Grant of Canada.}
    \tiny{We respectfully acknowledge that the UBC Okanagan academic campus is situated on the traditional, ancestral, unceded territory of the Syilx Okanagan Nation}
}

\subject{Nesterov's acceleration and its applications}

@@

            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}), and $\alpha_0 = 1, x_1 = v_1$, then they satisfy for all $k\ge 1$: 

@@

            Fix any arbitrary $x^* \in \RR^n$.

@@

            Then for all $k \ge 1$:
